\chapter{The $H\rightarrow W^{\pm}W^{\mp^*}$ Analysis}
\label{chap:hww}

% From Master
% Many different analyses were contributing to the big achievement of the experimental discovery of the Higgs boson in the year 2012 [5, 6]. The analysis of H → W±W∓∗ → `−  ̄ ν`+ν decays was an essential part of this success and nowadays still plays a major role in the Higgs boson physics programme at the LHC. This channel is so attractive because the Higgs boson decay into a pair of W bosons1 is the second most probable decay channel of the Higgs boson, with a branching fraction of 21.5%. By selecting leptons in the final state, additionally a good rejection power against background contributions is achieved.

Several analyses contributed to the great success of the experimental discovery of the Higgs boson in the year 2012. The analysis of \HWWdet\ decays was an essential part of this achievement. 
The \HWW decay is the second most probable decay channel, with a branching fraction of 21.5\%~\cite{PDG2020}, and if final states with two leptons are selected, good suppression of background contributions can be achieved.
This provides excellent opportunities for measurements of Higgs boson production cross sections.

The Higgs boson is mostly recognized as a result of the Higgs mechanism that provides masses to the $W$ and $Z$ bosons. 
It also solves another theoretical issue in the context of $WW$ scattering.
The cross section of the scattering of longitudinally polarized $W$ bosons ($W_LW_L \to W_LW_L$) diverges at high energies in the absence of the Higgs boson. In fact, the $WW$ scattering divergencies are cancelled only if the coupling of the Higgs boson to the $W$ bosons is exactly as predicted by the SM. Any observation of a different $HWW$ coupling would therefore require new physics to be introduced to keep the $WW$ scattering cross section finite. 
This provides extra motivation to study \HWW\ decays, in particular in their VBF production mode, as it is the most sensitive channel to measure the $HWW$ couplings at the LHC.

This chapter presents cross-section measurements of \HWWdet decays, with the Higgs boson produced via the ggF and VBF production mode, using the full dataset collected at \RunTwo of the LHC corresponding to 139\ifb. 
Prior measurements of these processes were performed by the ATLAS collaboration. 
The \HWW process was first observed using data from \RunOne of the LHC~\cite{HIGG-2013-13}, and an analysis of a partial \RunTwo dataset corresponding to 36.1\ifb reported the most recent measurements of ggF and VBF production cross sections~\cite{HIGG-2013-13}.
In the analysis presented here, several improvements compared to the previous \RunTwo results are implemented in addition to the increase in dataset size. Most noteworthy, the discrimination of the VBF signal is performed using a deep neural network (DNN) instead of a boosted decision tree, ggF signal events with two or more jets in the final state are included in the measurement, and measurements of cross sections in the kinematic regions defined by the STXS framework are reported for the first time.
The analysis is published in \ccite{HWWPaper} and yields some of the most precise Higgs cross-section meausurements to date.\footnote{The corresponding measurements based on the full \RunTwo dataset have been reported by the CMS collaboration in \ccite{Sirunyan_2021}.}
The results are also used as input to a combined Higgs boson measurement of the ATLAS collaboration where they make an essential contribution~\cite{NaturePaper}.

% This chapter starts with briefly reviewing previous measurements of \HWW decays conducted with smaller datasets and outlining the objectives of the updated measurements presented in this chapter. 
This chapter starts with a brief overview of the analysis and outlines the different signal categories measured. 
The relevant signal and background processes are characterized in detail in \cref{sec:signal-bkg-characteristics}. 
\Cref{sec:data-mc-samples} summarizes the data set and simulated samples used.
\Cref{sec:object-selection} discusses the criteria used to select the physics objects in the final state, and \cref{sec:event-categorization} outlines the details about how the events are selected and categorized. 
The background estimation techniques are explained in \cref{sec:bkg-estimation}. 
\Cref{sec:dnn} provides details on the development of a deep neural network to distinguish VBF, \HWW events from non-VBF signal events. 
\Cref{sec:systematics} discusses the derivation of all systematic uncertainties. 
\Cref{sec:stats-analysis} explains the statistical analysis that is used to extract the VBF and ggF signals, and \cref{sec:hww-results} presents the final results of the measurements.
\Cref{sec:conclusion} concludes this chapter.
It is worth noting, that the author's biggest contribution was to the analysis of \HWW events produced via VBF. In what follows, more details are therefore provided on the aspects related to the analysis of the VBF, \HWW events. 

% to cancel the $WW$ scattering divergencies. 
%This makes the \HWW\ decay of the Higgs boson particularly interesting to study. 
% This chapter presents the analysis of \HWWdet decays produced via the ggF and VBF production mode with data from \RunTwo of the LHC.
% The VBF, \HWW\ channel is particularly interesting, as it is the most sensitive channel to measure the $HWW$ couplings at the LHC. 

% - different flavor decays: introduce labelling: \HWWdet 
% - This chapter describes the details of the HWW measurement that went into the 10 year combination

%%%%%%%%%%%%%%%%%%
% Maybe add section: Overview of analysis and motivation?    
\section{Analysis Overview and Measurement Objectives}
\label{sec:analysis-overview}
The \HWW events that can be best separated from backgrounds at the LHC are the ones where the two $W$ bosons decay leptonically.
This analysis therefore analyzes events with two leptons in the final state. 
The most relevant background contributions come from $WW$ production, events with top quarks, $W$ production in association with jets ($W$+jets) where a jet is misidentified as a lepton, other diboson processes, and Drell-Yan processes. In particular Drell-Yan events are produced at large cross sections at the LHC. To reduce their contamination only final states with different-flavor leptons are selected, that is, with exactly one reconstructed muon and one electron.
Given the features of the signal and background processes, that are discussed in detail below, the analysis is divided into four signal categories separated by jet multiplicity and production mode.
Three categories target the ggF production mode (\emph{ggF signal}) by separating events into a \ZeroJet, \OneJet, and \TwoJet category, and one category targets the VBF production mode (\emph{VBF signal}), also requiring \TwoJet. 
This categorization is illustrated in \cref{fig:signal-categorization}. 
\TDinote{}{Maybe add nJet plot there with scaled ggF and VBF signal! Add flow chart with different regions}
Each of the categories is first optimized and validated separately before being statistically combined. 
The categories targeting the ggF signal use event selections to increase the purity of signal events. 
The VBF signal is discriminated using a DNN that distinguishes VBF signal from non-VBF signal events. 
The development of the DNN is described in \cref{sec:dnn}. 
To extract the signals and measure their cross sections times \HWW branching fraction, a likelihood fit is performed simultaneously in all categories. 
The signal yields are parametrized as signal strengths in the likelihood, 
\begin{equation}
    \label{eq:incl-ggF-VBF-signal-strengths}
    \mu_{\text{signal}} = \frac{ [ \sigma_{\text{signal}}  \times \BR(H \to WW^*) ]_\text{meas} } { [ \sigma_{\text{signal}} \times \BR(H \to WW^*) ]_\text{SM}}, 
\end{equation}
with the signal definition depending on the type of measurement that is performed.
The analysis presented performs three types of measurements:
\begin{itemize}
    \item Measurement of the inclusive VBF and ggF production cross sections by extracting two signal strengths $\mu_{\text{VBF}}$ and $\mu_{\text{ggF}}$.
    \item Measurement of the combined VBF and ggF production cross section, treating the VBF and ggF signal with a common signal strength $\mu_{\text{VBF+ggF}}$. 
    \item Measurement of differential cross sections separated in kinematic regions following the STXS framework. In total 11 signal strengths are measured targeting the ggF and VBF production mode. 
\end{itemize}
In addition, the excess of the VBF signal over the background expectation is reported in terms of its discovery significance, yielding, for the first time based on a single Higgs decay mode, the observation of the VBF production mode.
The results presented here supersede similar measurements performed with the same dataset but based on a previous version of the analysis~\cite{ATLAS-CONF-2021-014}.
The main differences between the analyses are changes in the simulated samples used, improved treatment of systematic uncertainties, and an improved DNN discriminant in the VBF category. 

% \section{Previous Results and Objectives of Measurement}
% \label{sec:prev-results}
% \input{\chapterdir/hwwsections/prev-results}

\section{Characteristics of the Signal and Background Processes}
\label{sec:signal-bkg-characteristics}
\input{\chapterdir/hwwsections/signal-bkg-characteristics}


\section{Data and Monte Carlo Samples}
\label{sec:data-mc-samples}
\input{\chapterdir/hwwsections/data-mc-samples}


\section{Object Identification and Sample Corrections}
\label{sec:object-selection}
\input{\chapterdir/hwwsections/object-selection}


\section{Event categorization}
\label{sec:event-categorization}
\input{\chapterdir/hwwsections/event-categorisation}


\section{Background Estimation}
\label{sec:bkg-estimation}
\input{\chapterdir/hwwsections/bkg-estimation}

\section{Discrimination of the VBF Signal with a Deep Neural Network}
\label{sec:dnn}
\input{\chapterdir/hwwsections/dnn}


\section{Systematic Uncertainties}
\label{sec:systematics}
\input{\chapterdir/hwwsections/systematics}


\section{The Statistical Model}
\label{sec:stats-analysis}
\input{\chapterdir/hwwsections/stats-analysis}


\section{Results}
\label{sec:hww-results}
\input{\chapterdir/hwwsections/results}

\section{Conclusion}
\label{sec:conclusion}
\input{\chapterdir/hwwsections/conclusion}